SpatialEpi

### 2016-08-20 README.Rmd
Updated README

```{r, message=FALSE, warning=FALSE}
plotmap(cases/population, sp.obj, log=TRUE, nclr=5)
points(grid2latlong(centroids), pch=4)
```

@@

# Compute output
# output <- bayes_cluster(y, E, population, sp.obj, centroids, max.prop,
#                         shape, rate, J, pi0, n.sim.lambda, n.sim.prior,
#                         n.sim.post)
```

```{r, cache=TRUE}
plotmap(output$post.map$high.area, sp.obj)
```

>>>>

```{r, message=FALSE, warning=FALSE, fig.height=8}
plotmap(cases/population, sp.obj, log=TRUE, nclr=5)
points(grid2latlong(centroids), pch=4)
```

@@

# Compute output
output <- bayes_cluster(y, E, population, sp.obj, centroids, max.prop,
                        shape, rate, J, pi0, n.sim.lambda, n.sim.prior,
                        n.sim.post)
```

```{r, cache=TRUE, fig.height=8}
plotmap(output$post_map$high_area, sp.obj)
```
